---
title: "MVPA_PTBUN_2023"
author: "Jacek Matuszewski"
date: '2023-09-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script loads csv accuracy outputs from `runMVPA_unimodal_ReadSpeech.m` and 
plots individual accuracies + group mean & SE per decoding condition in each ROI. 

Expected structure: 
outputs
    derivatives
        cosmo-mvpa
            <decoding_label> [mostly atlas or ROI type, e.g. 'visfatlas']
                accuracies [this is where your csv files should be ]
                permutations [not important for this script]
                confusion matrices [not important for this script]


decoding condition = pairwise decoding between each par of classes
Script should work even if you only have 1 (e.g. multiclass decoding)

This script will also calculate "group summaries" for accuracy (mean se) and print 
them on plots for convenience

Looking for ROIs, conditions and sensory modalities is done through `unique` function, 
so it's not hardcoded, it will just look for the unique values in your analyses

Load packages
```{r Load Packages}
library(tidyverse)
library(data.table)
library(cowplot)
library(RColorBrewer)
library(patchwork)
```


Set variables
```{r Setup variables}


ffx <- 'beta' # beta tmap
#featRatio <- '0.8' #just for saving outputs?
#space <-'IXI549Space'
FWHM <- 2
groups <- c('blind', 'sighted') # blind or sighted
# set te path to the task folder
stats_dir <- '/Volumes/Slim_Reaper/Projects/Language_MVPA/outputs/derivatives/bidspm-stats'

decoding_label <- 'JuBrain'#'visfatlas' #'cVWFA' 'LexPerVWFA' 'JuBrain'

roi_file_dir <- paste(stats_dir, 'derivatives','bidspm-groupStats', sep = '/')
roi_file_name <- paste0(decoding_label, '_stats.csv')

roi_fpath <- paste(roi_file_dir, roi_file_name, sep = '/')
```


Wrangle the ROI DF for plots

```{r DF wrangling and cleaning}
# EXPECTED STRUCTURE: LONG FORMAT WITH 1 COLUMN / ROI + 
# Condition, Group, Modality, Subject

# Get the raw csv file from MATLAB output and name the columns 
df.ROI.raw <- read_csv(roi_fpath, col_names = FALSE) %>% 
    rename(File = X1, 
           Group = X2, 
           ROI_file = X3, 
           Condition = X4, 
           ContrastEstimate = X5)

#Here you need to:
# 1. Extract the Subject ID from the file path - DONE
# 2. Extract the meaningfull non-BIDS ROI label from the BIDS name - DONE
# 3. Split the Condition into Condition and Modality on capital letter - DONE



df.ROI.clean <- df.ROI.raw %>% 
    #Get the subject name from file path
    mutate(Subject = str_split(File, "/", simplify = TRUE)[,9]) %>% 
    #Get the ROI label from ROI name
    mutate(ROI_label = str_split(ROI_file, "_", simplify = TRUE)[,4]) %>% 
    mutate(ROI_label = gsub(pattern = 'label-', replacement = '', ROI_label)) %>% 
    #Get proper Condition and Modality names 
    group_by(Condition) %>% 
    mutate(Modality = unlist(str_split(Condition, "(?=[[:upper:]])"))[2]) %>% 
    mutate(Modality = recode(Modality, 'Read' = 'Reading')) %>% 
    mutate(Condition = unlist(str_split(Condition, "(?=[[:upper:]])"))[3]) %>% 
    ungroup() %>% 
    # Capitalize Group names for plotting functions 
    mutate(Group = sub("(.)", "\\U\\1", Group, perl=TRUE)) %>% 
    # Change condition names
     mutate(Condition = recode(Condition, 'Word' = 'Words', 
                               'Pseudoword' = 'Pseudowords')) %>% 
    # Drop the File and ROI_name from the df 
    dplyr::select(Subject, Group, Modality, Condition, ROI_label, ContrastEstimate)
    

```


Summarize BOLD levels for descriptive purposes
```{r SUmmary Stats}
df.ROI.summaries <-  df.ROI.clean %>%
        group_by(Group, 
                 ROI_label,
                 Modality,
                 Condition) %>%
        dplyr::summarize(mean = mean(ContrastEstimate),
                                sd = sd(ContrastEstimate),
                                sem = sd(ContrastEstimate)/sqrt(n()),
                                .groups = 'keep')   
df.ROI.summaries
```

BAR PLOT TESTING 
```{r plot test, warning = FALSE}
#load plotting functions

# REMEMBER THAT COLORS FOR BARS ARE CODED AS 'FILL' NOT 'COLOUR'
# Colour = border
# so for bars its scale_fill_manual not scale_colour_manual! 

source('/Volumes/Slim_Reaper/Projects/Language_MVPA/code/src/cosmo-mpva/mvpa_plot_functions.R')

blind_triple_colors <- c(rep(c(brewer.pal(3, "Pastel2")[1], 
                         brewer.pal(3, "Set2")[1],   
                         brewer.pal(3, "Dark2")[1]),2))

sighted_triple_colors <- c(rep(c(brewer.pal(3, "Pastel2")[2], 
                           brewer.pal(3, "Set2")[2],   
                           brewer.pal(3, "Dark2")[2]),2))



plot.blind.Broca <- univariate_fMRI_ROI_bars(df.ROI.clean, 
                                             roi = 'Broca', 
                                             sub_group = 'Blind') 

plot.blind.Broca
```


PLOT LOOP! 
```{r Bar Plots}

#Get some prerequisits
source('/Volumes/Slim_Reaper/Projects/Language_MVPA/code/src/cosmo-mpva/mvpa_plot_functions.R')
dark_colors <- brewer.pal(n=3, name = "Dark2") 
#light_colors <- brewer.pal(n=3, name = "Pastel2") 
std.error <- function(x) sd(x)/sqrt(length(x))


# HERE YOU ALSO HAVE MODALITIES!
for (m in seq_along(modalities)){
    for(r in seq_along(roi)){
        for(g in seq_along(groups)){
            
            #Slice the df to get given roi, group & modality
            plot_df <- mvpa_joined%>% 
                filter(roiArea == roi[r],
                       group == groups[g],
                       modality == modalities[m]) 
            
            #Slice the average summary df 
            accu_df <- mvpa_accuracy %>% 
                filter(group == groups[g] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r])
            
            #make the basic plot with function
            plot_temp <- unimodal_mvpa_plot_ReadSpeech(plot_df, accu_df) 
            
            #recolour the plot based on group
            if (groups[g] == 'blind') {
                
                plot_temp <- plot_temp + 
                    scale_color_manual(values = c(rep(dark_colors[1], 3)))
                
            } else if (groups[g] == 'sighted') {
                
                plot_temp <- plot_temp + 
                    scale_color_manual(values = c(rep(dark_colors[2], 3)))
            }
            
            # assign new name to the sub plot 
            assign(paste0('plot_temp_', groups[g]), plot_temp)
            rm(plot_temp)
            
        }
        #PASTE THIS ROI AFTER BOTH GORUPS ARE DONE WITH PATCHWORK!
        plot_joined_temp <- plot_temp_blind + plot_temp_sighted
        
        assign(paste('plot_unimodal', roi[r], modalities[m], sep = '_'), plot_joined_temp)
        
        rm(plot_temp_blind, plot_temp_sighted, plot_joined_temp)
        
    }
}
```


Maybe add plot saving?

