---
title: "MVPA_PTBUN_2023"
author: "Jacek Matuszewski"
date: '2023-09-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script loads csv accuracy outputs from `runMVPA_unimodal_ReadSpeech.m` and 
plots individual accuracies + group mean & SE per decoding condition in each ROI. 

Expected structure: 
outputs
    derivatives
        cosmo-mvpa
            <decoding_label> [mostly atlas or ROI type, e.g. 'visfatlas']
                accuracies [this is where your csv files should be ]
                permutations [not important for this script]
                confusion matrices [not important for this script]


decoding condition = pairwise decoding between each par of classes
Script should work even if you only have 1 (e.g. multiclass decoding)

This script will also calculate "group summaries" for accuracy (mean se) and print 
them on plots for convenience

Looking for ROIs, conditions and sensory modalities is done through `unique` function, 
so it's not hardcoded, it will just look for the unique values in your analyses

Load packages
```{r}
library(tidyverse)
library(data.table)
library(cowplot)
library(RColorBrewer)
library(patchwork)
```


Set variables
```{r}


ffx <- 'beta' # beta tmap
#featRatio <- '0.8' #just for saving outputs?
#space <-'IXI549Space'
FWHM <- 2
groups <- c('blind', 'sighted') # blind or sighted
# set te path to the task folder
cosmo_results <- '/Volumes/Slim_Reaper/Projects/Language_MVPA/outputs/derivatives/cosmo-mvpa'
#task_audVis <-  paste('task-audVisMotSpatialFreq_space-MNI152NLin2009cAsym_FWHM-', as.character(FWHM), '_node-mvpaBlockAverage', sep ='')
task_ReadSpeech <- paste0('task-MultimodalReadSpeech_space-IXI549Space_FWHM-',as.character(FWHM),'_node-mvpa6betas')

decoding_label <- 'JuBrain'#'visfatlas' #'cVWFA' 'LexPerVWFA' 'JuBrain'
cosmo_results_path_ReadSpeech <- paste(cosmo_results, task_ReadSpeech,  decoding_label,
                                       'unimodal','accuracy', sep ='/')

#namePattern <- paste('sub-',group,'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
```


Load results and create group DFs
```{r}
for(g in seq_along(groups)) {
    
    #Set name pattern and get the files
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAcrossmodal_.*\\.csv$', sep = '')
    namePattern <- paste('sub-',groups[g],'.*_label-',decoding_label,'_.*\\.csv$', sep = '')
    
    allfiles_ReadSpeech <- list.files(cosmo_results_path_ReadSpeech, pattern = namePattern)
    
    group_df_temp <- lapply(paste(cosmo_results_path_ReadSpeech, 
                                  allfiles_ReadSpeech, sep ='/'), 
                            read.csv, sep =',') %>% 
        rbindlist %>% 
        dplyr::select(!contains('permutation')) %>% 
        mutate(accuracy = accuracy * 100) %>% #make %
        mutate(group = groups[g])#drop the null distribution columns %>%
    
        
    #Rename the group DF
    assign(paste0('mvpa_',groups[g]), group_df_temp)
    rm(group_df_temp)
}

#join the dfs
mvpa_joined <- rbind(mvpa_blind, mvpa_sighted) %>% 
    mutate(conditions = factor(conditions, levels = c('WordPseudoword', 'WordControl',
                                                      'PseudowordControl')))
rm(mvpa_blind, mvpa_sighted)

```


Specify plotting variables based on the MVPA content (ROIs, decoding conditions)
assumes identical variables between groups! 
```{r}
#Name of ROIs 
roi <- unique(mvpa_joined$roiArea)

#Name of decoding conditions 
classifier <- unique(mvpa_joined$conditions)
modalities <- unique(mvpa_joined$modality)
```

Summarize accuracies for descriptive purposes
```{r}
mvpa_accuracy <-  mvpa_joined %>%
     mutate(conditions = factor(conditions, levels = classifier)) %>% 
        group_by(group, 
                 roiArea,
                 ffxResults,
                 modality,
                 conditions) %>%
        summarize(mean_accuracy = mean(accuracy),
                                sd_accurarcy = sd(accuracy),
                                se_accuracy = sd(accuracy)/sqrt(20),
                                .groups = 'keep')   
```


PLOTTING FOR BOTH GROUPS  (pasted next to each other)
```{r}

dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 
std.error <- function(x) sd(x)/sqrt(length(x))

#for(g in seq_along(groups)) {
    for(m in seq_along(modalities)) {
      # for(c in seq_along(classifier)) {
            for (r in seq_along(roi)) {
        
            accu_bl <- mvpa_accuracy %>% 
                filter(group == 'blind' & 
                           #conditions == classifier[c] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r])
            
            accu_sig <- mvpa_accuracy %>% 
                filter(group == 'sighted' & 
                           #conditions == classifier[c] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r])
                
                
           plot_bl <- 
                mvpa_joined %>% 
                # Pick a condition and modality for this plot
                filter(group == 'blind' & 
                           #conditions == classifier[c] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r]) %>% 
                ggplot(aes(x = conditions, y = accuracy, color = roiArea)) +
                geom_point(aes(alpha = I(0.7)), 
                   position = position_jitterdodge(jitter.width=0.2,
                                                   dodge.width = 0.3),
                   size = 4.5) +
                stat_summary(aes(x =conditions, y = accuracy, color = roiArea),
                     fun = "mean", 
                     geom = "crossbar", 
                     position = position_dodge(width = 0.5),
                     width = .55,
                     colour  = 'black',
                     inherit.aes = FALSE,
                    show.legend = FALSE) + 
                stat_summary(aes(x = conditions, y = accuracy, color = roiArea),
                         fun.max = function(x) mean(x) + (std.error(x)), # sems too small for sighted
                         fun.min = function(x) mean(x) - (std.error(x)), # sems too small for sighted
                         #fun.max = function(x) mean(x) + sd(x),
                         #fun.min = function(x) mean(x) - sd(x),
                         geom = "errorbar",
                         position = position_dodge(width = 0.5),
                         width = .15,
                         size = 0.8,
                         colour  = 'black',
                         inherit.aes = FALSE,
                         show.legend = FALSE) + 
                geom_hline(yintercept=c(50), 
                       linetype="dotted", 
                       colour="black", 
                       linewidth=.5) +
                scale_color_manual(values = c(rep(dark_colors[1], 3))) +
                scale_y_continuous(name = "Clasisfier Accuracy [%]", 
                                   limits = c(0,100)) +
                scale_x_discrete(name = 'Decoding conditions') +
                annotate("text", 
                         x = classifier, 
                         y = 5, 
                         label = c(round(accu_bl$mean_accuracy, digits = 2)))+
                annotate("text", 
                         x = classifier, 
                         y = 0, 
                         label = c(round(accu_bl$se_accuracy, digits = 2))) +
                theme_cowplot(font_size = 16, font_family = "Arial") +
                theme(axis.line = element_line(colour = 'black', size = 1),
                      axis.ticks = element_line(colour = 'black', size = 1),
                      axis.text = element_text(face="bold"),
                      legend.position = 'none')
           
           plot_sig <- 
                mvpa_joined %>% 
                # Pick a condition and modality for this plot
                filter(group == 'sighted' & 
                           #conditions == classifier[c] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r]) %>% 
                ggplot(aes(x = conditions, y = accuracy, color = roiArea)) +
                geom_point(aes(alpha = I(0.7)), 
                   position = position_jitterdodge(jitter.width=0.2,
                                                   dodge.width = 0.3),
                   size = 4.5) +
                stat_summary(aes(x =conditions, y = accuracy, color = roiArea),
                     fun = "mean", 
                     geom = "crossbar", 
                     position = position_dodge(width = 0.5),
                     width = .55,
                     colour  = 'black',
                     inherit.aes = FALSE,
                    show.legend = FALSE) + 
                stat_summary(aes(x = conditions, y = accuracy, color = roiArea),
                         fun.max = function(x) mean(x) + (std.error(x)), # sems too small for sighted
                         fun.min = function(x) mean(x) - (std.error(x)), # sems too small for sighted
                         #fun.max = function(x) mean(x) + sd(x),
                         #fun.min = function(x) mean(x) - sd(x),
                         geom = "errorbar",
                         position = position_dodge(width = 0.5),
                         width = .15,
                         size = 0.8,
                         colour  = 'black',
                         inherit.aes = FALSE,
                         show.legend = FALSE) + 
                geom_hline(yintercept=c(50), 
                       linetype="dotted", 
                       colour="black", 
                       linewidth=.5) +
                scale_color_manual(values = c(rep(dark_colors[2], 3))) +
                scale_y_continuous(name = "Clasisfier Accuracy [%]", 
                                   limits = c(0,100)) +
                scale_x_discrete(name = 'Decoding conditions') +
                annotate("text", 
                         x = classifier, 
                         y = 5, 
                         label = c(round(accu_sig$mean_accuracy, digits = 2)))+
                annotate("text", 
                         x = classifier, 
                         y = 0, 
                         label = c(round(accu_sig$se_accuracy, digits = 2))) +
                theme_cowplot(font_size = 16, font_family = "Arial") +
                theme(axis.line = element_line(colour = 'black', size = 1),
                      axis.ticks = element_line(colour = 'black', size = 1),
                      axis.text = element_text(face="bold"),
                      legend.position = 'none')
            
           plot <- plot_bl + plot_sig    
                           
            #Rename the plot based on what it represents 
            assign(paste('plot_unimodal', roi[r], modalities[m],  
                         sep = '_'), plot)
            rm(plot, plot_bl, plot_sig)
            
            }
      # }
   }
#}

```


Plotting individually for each group / ROI
```{r}
# 
# dark_colors <- brewer.pal(n=3, name = "Dark2") 
# light_colors <- brewer.pal(n=3, name = "Pastel2") 
# std.error <- function(x) sd(x)/sqrt(length(x))
# 
# for(g in seq_along(groups)) {
#     for(m in seq_along(modalities)) {
#       # for(c in seq_along(classifier)) {
#             for (r in seq_along(roi)) {
#         
#             accu <- mvpa_accuracy %>% 
#                 filter(group == groups[g] & 
#                            #conditions == classifier[c] & 
#                            modality == modalities[m] & 
#                            ffxResults == ffx &
#                            roiArea == roi[r])
#                 
#                 
#            plot <- 
#                 mvpa_joined %>% 
#                 # Pick a condition and modality for this plot
#                 filter(group == groups[g] & 
#                            #conditions == classifier[c] & 
#                            modality == modalities[m] & 
#                            ffxResults == ffx &
#                            roiArea == roi[r]) %>% 
#                 ggplot(aes(x = conditions, y = accuracy, color = roiArea)) +
#                 geom_point(aes(alpha = I(0.7)), 
#                    position = position_jitterdodge(jitter.width=0.2,
#                                                    dodge.width = 0.3),
#                    size = 4.5) +
#                 stat_summary(aes(x =conditions, y = accuracy, color = roiArea),
#                      fun = "mean", 
#                      geom = "crossbar", 
#                      position = position_dodge(width = 0.5),
#                      width = .55,
#                      colour  = 'black',
#                      inherit.aes = FALSE,
#                     show.legend = FALSE) + 
#                 stat_summary(aes(x = conditions, y = accuracy, color = roiArea),
#                          fun.max = function(x) mean(x) + (std.error(x)), # sems too small for sighted
#                          fun.min = function(x) mean(x) - (std.error(x)), # sems too small for sighted
#                          #fun.max = function(x) mean(x) + sd(x),
#                          #fun.min = function(x) mean(x) - sd(x),
#                          geom = "errorbar",
#                          position = position_dodge(width = 0.5),
#                          width = .15,
#                          size = 0.8,
#                          colour  = 'black',
#                          inherit.aes = FALSE,
#                          show.legend = FALSE) + 
#                 geom_hline(yintercept=c(50), 
#                        linetype="dotted", 
#                        colour="black", 
#                        linewidth=.5) +
#                 scale_color_manual(values = if(groups[g] == 'blind'){
#                     c(rep(dark_colors[1], 3))
#                 } else if(groups[g] == 'sighted') {
#                     c(rep(dark_colors[2], 3))
#                 }) +
#                 scale_y_continuous(name = "Clasisfier Accuracy [%]", 
#                                    limits = c(0,100)) +
#                 scale_x_discrete(name = 'Decoding conditions') +
#                # ggtitle(paste(groups[g], modalities[m], classifier[c], sep = ' ')) +
#                # TRY TO ANNOTATE THE PLOTS WITH MEAN AND SEM VALUES? 
#                 annotate("text", 
#                          x = classifier, 
#                          y = 5, 
#                          label = c(round(accu$mean_accuracy, digits = 2)))+
#                 annotate("text", 
#                          x = classifier, 
#                          y = 0, 
#                          label = c(round(accu$se_accuracy, digits = 2))) +
#                 theme_cowplot(font_size = 16, font_family = "Arial") +
#                 theme(axis.line = element_line(colour = 'black', size = 1),
#                       axis.ticks = element_line(colour = 'black', size = 1),
#                       axis.text = element_text(face="bold"),
#                       legend.position = 'none')
#                 
#                            
#             #Rename the plot based on what it represents 
#             assign(paste('plot_unimodal',groups[g], roi[r], modalities[m],  
#                          sep = '_'), plot)
#             rm(plot)
#             
#             }
#       # }
#    }
# }

```



